---
title: "pa4"
author: "Hyunjung Joo"
institute: "Rutgers University"
output:
  xaringan::moon_reader:
    lib_dir: libs
    nature:
      highlightStyle: github
      highlightLines: true
      countIncrementalSlides: false
      ratio: "16:9"
---

#1. Setup and data load
```{r setup, include=TRUE, message=FALSE, warning=FALSE}
library("tidyverse")
library("ds4ling")
library("patchwork")
library("ggfortify")
library("ggplot2")
library("lmtest")
library("here")
library("untidydata")
library("broom")
```

```{r, load-data, message=FALSE, out.width="50%", fig.height=3, fig.retina=2}

data <- read_csv(file = here("data_raw", "fricatives","fricatives.csv"))

```
---
#2. Tidying the data
```{r, tidy, message=FALSE,message=FALSE, out.width="50%", fig.height=3, fig.retina=2}

data_tidy <- data %>%
  pivot_longer(, col = c("s_cog","sh_cog","s_skewness","sh_skewness"),
               names_to = "names", 
               values_to = "values") %>%
  separate(names, c("phoneme", "measure"), "_") %>%
  write_csv(file = here("data_tidy", "fricatives_tidy.csv"))
head(data_tidy)
```
---
#3. Descriptive statistics
```{r, message=FALSE}

data_tidy %>%
  group_by(phoneme, measure) %>%
  summarize(avg = mean(values),
            sd = sd(values)) %>%  
  mutate_if(is.numeric, round, digits = 2) %>%
  knitr::kable()

```
---
#4. Center of gravity as a function of Phoneme
```{r, message=FALSE, out.width="400px", out.height="350px",fig.align='center'}
data_v2 <- data_tidy %>%
  pivot_wider(., names_from = "measure", values_from = "values")
data_v2 %>%
  ggplot(aes(x = phoneme, y = cog)) +
  geom_boxplot() + labs(x = "Phoneme", y = "Center of gravity") 

```
---
#5. Skewness as a function of Phoneme

```{r, message=FALSE, out.width="400px", out.height="350px", fig.align='center'}
data_v2 %>%
  ggplot(aes(x = phoneme, y = skewness)) +
  stat_summary(fun.data = mean_se, geom = "errorbar", width = .25) +
  stat_summary(fun = mean, geom = "point", size = 4, fill='black', pch = 21) +
  labs(x = "Phoneme", y = "Skewness") 
```
---
#6. Center of gravity as a function of skewness for [s]
###Statistical analysis
```{r, message=FALSE}
data_wide <- data_v2 %>%
  pivot_wider(.,names_from = phoneme, values_from = c(cog, skewness))

mod1 <- lm(cog_s ~ skewness_s, data = data_wide)
tidy(mod1) %>% 
  mutate_if(is.numeric, round, digits = 2) %>%
  knitr::kable()
```
---
#6. Center of gravity as a function of skewness for [s]
###Plot
```{r, message=FALSE, out.width="400px", out.height="350px", fig.align='center'}
data_wide %>%
  ggplot(aes(x = skewness_s, y = cog_s)) +
  geom_point() + geom_smooth(method = "lm")
```
---
#7. Diagnostics
###The mean of residuals is zero
```{r, message=FALSE}
summary(mod1$residuals) 

```
---
#7. Diagnostics
###Homoskedasticity and normality of residuals
```{r, message=FALSE,out.width="90%", fig.height=2.5, fig.align='center'}
autoplot(mod1, which = c(1,2))
```
---
#7. Diagnostics
###No autocorrelation of residuals
```{r, message=FALSE, out.width="400px", out.height="350px", fig.align='center'}
acf(mod1$residuals) 
```
---
#7. Diagnostics
###No autocorrelation of residuals
```{r, message=FALSE, echo=FALSE}
lmtest::dwtest(mod1)
```
---
#7. Diagnostics
###Predictors and residuals are uncorrelated
```{r, message=FALSE}
cor.test(data_wide$skewness_s, mod1$residuals)
```
---
#8. Results
###General description
The production data for fricatives were analyzed using a linear model to test the effect of *Skewness* for [s] segment on *Center of gravity*. *Center of gravity* was included as a dependent variable, while *Skewness* was included as a fixed effect. Visual inspection of Q-Q plots and plots of residuals against fitted values revealed no discernable deviations from normality and homoskedasticity. Multiple and adjusted R-squared are provide for the indication of goodness of fit for the model. p-values less than .05 were reported as significant.

###Results
The table in slide 7 summarizes *Center of gravity* as a function of *Skewness* for [s] segment. The model accounted for the variance for 88% (Multiple R-squared:  0.88, Adjusted R-squared:  0.87). As illustrated in the graph in slide 8, *Center of gravity* showed a linear relationship with *Skewness* for [s] segment (b = 3029.1, SE: 259.1, t = 11.69, p <.001). Specifically, as for [s] segment, one unit change in skewness was associated with an increase of center of gravity by 3029. Thus, the results show that when *Skewness* increases, *Center of gravity* increases in a linear way.

---
#9. Assumptions.csv
.pull-left[
```{r, message=FALSE, out.width="400px", out.height="350px", fig.align='left'}
assumptions <- read_csv(file = here("data_raw", "fricatives", "assumptions.csv"))
assumptions %>%
  ggplot(aes(x, y)) + geom_point()
```
]
.pull-right[
As shown in the plot on the left, there is neither linear or non-linear relationship between *x* and *y*. There is no particular pattern of *y* as a function of *x*, because there are multiple values of *y* that correspond to the same *x*. Therefore, there is no model that fits this data. 
]